Succinct representations for abstract interpretation

### 2011-11-02 papers/PLDI2012/implicitization.tex
mauvaise citation

Statistically, the domain of convex polyhedra gives the better results, but
commonly yields weaker invariants than the domains of octagons/intervals;
this is a known weakness of its widening operator~\cite{Monniaux_LeGuen2011}.
The Octagon domain appears to be much better than intervals; this is
unsurprising since in most programs and libraries, bounds on loop indices are
non constant: they depend on some parameters (array sizes etc.).

>>>>

Statistically, the domain of convex polyhedra gives the better results, but
commonly yields weaker invariants than the domains of octagons/intervals;
this is a known weakness of its widening operator~\cite{Monniaux_LeGuen2011}. 
\JH{la citation n'est pas bonne. On tombe sur ``Automatic Modular Abstractions for Template Numerical Constraints''}
The Octagon domain appears to be much better than intervals; this is
unsurprising since in most programs and libraries, bounds on loop indices are
non constant: they depend on some parameters (array sizes etc.).
